Using traffic analysis to identify The Second Generation Onion Router

### 2011-04-17 thesis/experiment.tex
Added software versions.

  Most modern network appliances used for routing, even those labelled as hubs,
  include switching capabilities, which means that packets routed are only
  delivered to the addressed host. This makes eavesdropping difficult. For
  the purpose of this experiment a simple hub or repeater is required. A hub
  does not examine packet delivery information, it simple broadcasts all packets
  received to every connected port, allowing for passive eavesdropping without
  complicated network configuration \parencite{website:hub-reference}.

@@

  The tcpdump software captures network packets that are transferred using
  network interfaces attached to the current hardware \parencite{:2009cr}.  It is
  available on most operating systems and supports a flexible filtering language
  for capturing only the specific packets desired. The format of output produced
  by tcpdump is well documented \parencite{:nx} which makes it ideal for
  transformation and processing by third party tools.

@@

  VirtualBox software allows multiple guest operating systems to run in an
  isolated virtual environment on a host operating system \parencite{:fk}.
  It is free software and supports both snapshots and a remote control facility
  which make it useful for running a controlled experiment \parencite{Oracle:2011kx}.

@@

  Ruby is an object orientated, dynamic programming language which is useful for
  rapid prototyping and is supported by a large community that has developed
  powerful add on software in the form of Ruby Gems \parencite{:2010uq}. These
  Gems include support for the Selenium browser testing framework, process
  monitoring, dynamic web content generation and automated testing.

@@

  The Ubuntu Linux operating system is freely available Linux operating system
  available for desktop personal computers \parencite{:2010ly}. It comes
  packaged with the 'tcpdump' software and can be configured in a reliable and
  consistent way with typical set of POSIX tools and the 'apt-get' package
  manager \parencite{Pereira:2011uq}.

@@

  Selenium is a web testing framework which allows automated testing of web pages
  through any Javascript enabled web browser \parencite{:2010ys}. A web browser
  can be controlled remotely using the Selenium Remote Control Server component,
  which in turn can be controlled with a number of programming languages including
  Ruby. Using Selenium the typical interactions a user makes when viewing a
  website can be simulated.

@@

  Firefox is a web browser developed by the Mozilla organization and freely
  available for most desktop personal computers \parencite{Foundation:2011fk}.
  It's strong standards compliance \parencite{Hammond:2010fk} and popularity
  \parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
  candidate for this experiment.

@@

  OpenSSH is a freely available suite of connectivity tools
  \parencite{:2010zr,:ve} that supports remote command execution
  \parencite{Tucker:2010ly}. The client component of OpenSSH is installed by
  default on the Ubuntu operating system and the server component is easily
  installed using the apt-get package management system.

@@

  The Apache web server is the most prevalent web server used on the Internet
  \parencite{2010:dq}. The Apache web server can serve static web content over
  both the HTTP and HTTPS protocols \parencite{Foundation:2011uq}. Combined with
  software such as Sinatra it can serve dynamic web content.

@@

  Sinatra is a simple framework for creating dynamic web applications using the
  Ruby programming language \parencite{:2010bh}. Sinatra requires very little
  configuration and development time to develop dynamic web applications.

@@

  RSpec is a behaviour driven testing framework for Ruby which allows the
  creation of examples in an easy to read Domain Specific Language (DSL)
  \parencite{Chelimsky:2010vn}. It is well integrated with Selenium which makes
  it ideal for running large suites of Selenium tests.

>>>>

  Most modern network appliances used for routing, even those labelled as hubs,
  include switching capabilities, which means that packets routed are only
  delivered to the addressed host. This makes eavesdropping difficult. For
  the purpose of this experiment a Netgear DS106 dual speed hub was used. A hub
  does not examine packet delivery information, it simple broadcasts all packets
  received to every connected port, allowing for passive eavesdropping without
  complicated network configuration \parencite{website:hub-reference}.

@@

  The tcpdump software captures network packets that are transferred using
  network interfaces attached to the current hardware \parencite{:2009cr}.  It is
  available on most operating systems and supports a flexible filtering language
  for capturing only the specific packets desired. The format of output produced
  by tcpdump is well documented \parencite{:nx} which makes it ideal for
  transformation and processing by third party tools. Tcpdump version 4.0.0
  combined with libpcap 1.0.0 was used for this experiment.

@@

  VirtualBox software allows multiple guest operating systems to run in an
  isolated virtual environment on a host operating system \parencite{:fk}.
  It is free software and supports both snapshots and a remote control facility
  which make it useful for running a controlled experiment \parencite{Oracle:2011kx}.
  VirtualBox version 3.2.6 r63112 was used in this experiment.

@@

  Ruby is an object orientated, dynamic programming language which is useful for
  rapid prototyping and is supported by a large community that has developed
  powerful add on software in the form of Ruby Gems \parencite{:2010uq}. These
  Gems include support for the Selenium browser testing framework, process
  monitoring, dynamic web content generation and automated testing. The Ruby
  1.8.7 (2010-01-10 patchlevel 249) Ubuntu package was installed where Ruby was
  required. The exact version of all gems used in the experiment are shown in
  table \ref{table:gems}.

  \begin{center}
    \begin{minipage}[t]{\linewidth}
      \begin{table}[H]
        \begin{tabular}{llr}
          \toprule
          Gem name & Purpose & Version \\
          \midrule
          bundler & Application gem manager & 1.0.2 \\
          daemon\_controller & Monitor and control daemon processes & 0.2.6 \\
          rspec & Testing and control of selenium & 1.3.0 \\
          selenium-client & Control browser using selenium and ruby & 1.2.18 \\
          haml & A simple HTML like markup language & 3.0.21 \\
          rack & Rack web serving framework & 1.2.1 \\
          sinatra & Ruby web framework & 1.0 \\
          \bottomrule
        \end{tabular}
        \caption{Ruby Gems}
        \label{table:gems}
      \end{table}
    \end{minipage}
  \end{center}

@@

  The Ubuntu Linux operating system is freely available Linux operating system
  available for desktop personal computers \parencite{:2010ly}. It comes
  packaged with the 'tcpdump' software and can be configured in a reliable and
  consistent way with typical set of POSIX tools and the 'apt-get' package
  manager \parencite{Pereira:2011uq}. Both the desktop and server editions were
  used for this experiment, version 10.04 commonly referred to as lucid lynx.

@@

  Selenium is a web testing framework which allows automated testing of web pages
  through any Javascript enabled web browser \parencite{:2010ys}. A web browser
  can be controlled remotely using the Selenium Remote Control Server component,
  which in turn can be controlled with a number of programming languages including
  Ruby. Using Selenium the typical interactions a user makes when viewing a
  website can be simulated. Selenium version 1.0.6 was used for this experiment.

@@

  Firefox is a web browser developed by the Mozilla organization and freely
  available for most desktop personal computers \parencite{Foundation:2011fk}.
  It's strong standards compliance \parencite{Hammond:2010fk} and popularity
  \parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
  candidate for this experiment. The Ubuntu Firefox package was used in this
  expriment, version 3.6.8.

@@

  OpenSSH is a freely available suite of connectivity tools
  \parencite{:2010zr,:ve} that supports remote command execution
  \parencite{Tucker:2010ly}. The client component of OpenSSH is installed by
  default on the Ubuntu operating system and the server component is easily
  installed using the apt-get package management system. The version used for
  this experiment was OpenSSH\_5.3p1 Debian-3ubuntu4, OpenSSL 0.9.8k 25 Mar 2009.

@@

  The Apache web server is the most prevalent web server used on the Internet
  \parencite{2010:dq}. The Apache web server can serve static web content over
  both the HTTP and HTTPS protocols \parencite{Foundation:2011uq}. Combined with
  software such as Sinatra it can serve dynamic web content. Apache version
  2.2.14/Ubuntu was used to serve web sites in this experiment.

@@

  Sinatra is a simple framework for creating dynamic web applications using the
  Ruby programming language \parencite{:2010bh}. Sinatra requires very little
  configuration and development time to develop dynamic web applications.
  Sinatra version 1.0 was used in this experiment.

@@

  RSpec is a behaviour driven testing framework for Ruby which allows the
  creation of examples in an easy to read Domain Specific Language (DSL)
  \parencite{Chelimsky:2010vn}. It is well integrated with Selenium which makes
  it ideal for running large suites of Selenium tests. RSpec version 1.3.0 was
  used in this experiment.
